---
title: "tableone introduction"
description: |
  I followed the "Introduction to tableone" notes by Kazuki Yoshida (see: https://cran.r-project.org/web/packages/tableone/vignettes/introduction.html)
author:
  - name: Bonnie Butler
    url: {}
date: 2021-03-07
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load tableone package
```{r}
library(tableone)
library(distill)
```

# Load survival package for Mayo Clinic's PBC data
```{r}
library(survival)
data(pbc)
```

# Single group summary
# Simplest use case
```{r}
CreateTableOne(data = pbc)
```
# Categorical variable conversion
# Get variable names
```{r}
dput(names(pbc))
```

# Vector of variables to summarise
```{r}
myVars <- c("time", "status", "trt", "age", "sex", "ascites", "hepato", "spiders", "edema", "bili", "chol", "albumin", "copper", "alk.phos", "ast", "trig", "platelet", "protime", "stage")
```
# Vector of categorical variables that need transformation
```{r}
catVars <- c("status", "trt", "ascites", "hepato", "spiders", "edema", "stage")
```
# Create a TableOne object
```{r}
tab2 <- CreateTableOne(vars = myVars, data = pbc, factorVars = catVars)
```

# Showing all levels for categorical variables
```{r}
print(tab2, showAllLevels = TRUE, formatOptions = list(big.mark = ","))
```
# Detailed information including missingness
```{r}
summary(tab2)
```
# Summarising nonnormal variables
```{r}
biomarkers <- c("bili", "chol", "copper", "alk.phos", "trig", "protime")
print(tab2, nonnormal = biomarkers, formatOptions = list(big.mark = ","))
```
# Multiple group summary
```{r}
tab3 <- CreateTableOne(vars = myVars, strata = "trt", data = pbc, factorVars = catVars)
print(tab3, nonnormal = biomarkers, formatOptions = list(big.mark = ","))
```
# Testing
```{r}
print(tab3, nonnormal = biomarkers, exact = "stage", smd = TRUE)
```
# Miscellaneous
# Categorical or continuous variables-only

# Categorical part only
```{r}
tab3$CatTable
```
# Continuous part only
```{r}
print(tab3$ContTable, nonnormal = biomarkers)
```