---
title: "tableone palmerpenguins"
description: |
  Using the TableOne instructions from (https://cran.r-project.org/web/packages/tableone/vignettes/introduction.html) on the palmerpenguins package.
author:
  - name: Bonnie Butler
    url: {}
date: 2021-03-07
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r}
library(tableone)
library(tidyverse)
library(palmerpenguins)
```

# Read datasets
```{r}
data(penguins)
```

# Single group summary
# Simplest use case
```{r}
CreateTableOne(data = penguins)
```
# Categorical variable conversion
# Get variable names
```{r}
dput(names(penguins))
```
# Vector of variables to summarise
```{r}
myVars <- c("species", "island", "bill_length_mm", "bill_depth_mm", "flipper_length_mm", "body_mass_g", "sex", "year")
```
# Vector of categorical variables that need transformation
```{r}
catVars <- c("species", "island", "sex", "year")
```
# Create a TableOne object
```{r}
tab2 <- CreateTableOne(vars = myVars, data = penguins, factorVars = catVars)
```

# Showing all levels for categorical variables
```{r}
print(tab2, showAllLevels = TRUE, formatOptions = list(big.mark = ","))
```
# Detailed information including missingness
```{r}
summary(tab2)
```
# Multiple group summary
```{r}
tab3 <- CreateTableOne(vars = myVars, strata = "species", data = penguins, factorVars = catVars)
print(tab3, formatOptions = list(big.mark = ","))
```
# Testing
```{r}
print(tab3, exact = "year", smd = TRUE)
```

# Miscellaneous
# Categorical or continuous variables-only
# Categorical part only
```{r}
tab3$CatTable
```
# Continuous part only
```{r}
print(tab3$ContTable)
```


